\documentclass[a4paper,12pt]{article}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}


%% Sets page size and margins
%\usepackage[a4paper,top=1cm,bottom=4mm,left=3cm,right=0mm,marginparwidth=1.75cm]{geometry}
%\usepackage[a4paper,top=0cm,bottom=3mm,left=3mm,right=0mm,marginparwidth=0cm]{geometry}
\usepackage{geometry} % for \newgeometry{} and \restoregeometry

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{url}%for \path{}
\usepackage{lscape}
\pagenumbering{gobble}%no numbers in the webpage
%\usepackage[counterclockwise]{rotating} %sidewaysfigure

%\graphicspath{{/home/map479/mxochicale/github/DataSets/emmov/plots_timeseries/openface/}}
%\title{ OpenFace Time Series }

\title{Observations for emmov-pilotstudy}
\author{Miguel P Xochicale \\
School of Engineering\\
University of Birmingham, UK}


\begin{document}
\newgeometry{top=20mm,bottom=20mm,left=20mm,right=20mm}
\maketitle

%\begin{abstract}
%Time series for Facial Action Units. 
%\end{abstract}



\section{Razor}

\begin{enumerate}
\item Data from the inertial sensor got problems in the syncronisation
	and the collection of data from four sensors in seven experiments.
	Only three of the experiments collected data for the four inertial sensors, 
	and the other four only collected data from three sensors. Such problems 
	are related to the poor bluetooth connection between sensors and 
	the bluetooth dongle (21 February 2018).

\end{enumerate}


\section{Open Face}

\begin{enumerate}
\item One general observation from the face landmarks is that 
	movements of the head pose translation position (pose Tx and pose Ty) 
	are mounted in all the face landmarks (x\_0 to x\_67) (21 February 2018).

\item For future experiments with \cite{baltrusaitis2016}, the camera 
	should be put as closer as can be to the face of the person 
	in order to get better estimation of facelandmarks (21 February 2018).

\item Just by eye, I cannot see evidently differences when observing the time series for
 	postprocessing data. The most evident is the sgconfidence and sgsuccess for which
 	participants p03 and p04 failed to track their head pose estimation and face landmarks.
 	Pose time series also represent a good indicator for head movement which can be seen
	in the inestability of  participant three with the ocuclision problems and
 	participant five which was quite  static in the activity.
	(28 February 2018).



\end{enumerate}


The data for the current pilot study is available in \cite{mxochicale2018}.








\bibliographystyle{apalike}
\bibliography{references}

%\newpage

%\newgeometry{top=0cm,bottom=3mm,left=3mm,right=0mm,marginparwidth=0cm}
%\restoregeometry







\end{document}
